Investigation of the Effect of Pretraining on EEG Classification with Deep Recurrent-Convolutional Networks

### 2017-10-15 paper/paper.tex
Add abstract, title, authors, fix graphics

\title{TITLE}
\author{Authors}

@@

\section*{Abstract}
abstract content

@@

\includegraphics{inputs_orig}

@@

\includegraphics{elu}

@@

@@

\includegraphics{denoising}

@@

\includegraphics{mask}

>>>>

\title{Investigation of the Effect of Pretraining on EEG Classification with Deep Recurrent-Convolutional Networks}
\author{Castle, Steffen \and Harbecke, David \and Rakowski, Alexander \and Stazherova, Maria}

@@

\section*{Abstract}
The purpose of this research project is to investigate the use of deep neural networks in classification of EEG recordings. For this task we developed a model based on the architecture proposed by Bashivan et al. \cite{learning_eeg_repr}, with modifications for pretraining in the convolutional stage and bidirectionality in the LSTM stage. We trained and evaluated our model on a dataset consisting of EEG recordings labeled by subject. Our model showed improvement over the model proposed by Bashivan et al., with over 89\% accuracy on the task of classifying EEG recordings by subject.

@@

	\centering
    \includegraphics[scale=0.6]{inputs_orig}

@@

    \centering
    \includegraphics[scale=0.75]{elu}

@@

    \centering

@@

    \centering
    \includegraphics[scale=0.75]{denoising}

@@

    \centering
    \includegraphics[scale=0.55]{mask}
